Kindly Bent to Free Us

### 2019-02-21 kindly/infer/infer.tex
Add typing for pairs and complete the kinds/lattices.

\begin{figure*}[tp]
  \input{infer/entails}
  \caption{Base entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure*}

@@

\begin{figure}[tp]\centering
\begin{align*}
  \Sv\cap\Sv'
  &= \left\{ x \to l,l'
    \mid \Sone{x}{l}\in\Sv \text{ and } \Sone{x}{l'}\in\Sv' \right\} \\
  \Sv\cup\Sv'
  &= \Sv\cap\Sv' \sqcup
    (\Sv\Sdel{x' \mid x'\in\Sv'}) \sqcup
    (\Sv'\Sdel{x \mid x\in\Sv})
  &\text{where $\sqcup$ is the disjoint union}\\
  \Cleq{\Sv}{k_0}
  &= \bigwedge_{\Sone{x}{l_x}\in\Sv} \bigwedge_{k\in l_x} \Cleq{k}{k_0}
\end{align*}
\caption{Operation on usage maps $\Sv$}
\label{op:usgmap}
\end{figure}

@@

\newcommand\lub\bigvee
\newcommand\glb\bigwedge
\newcommand\CL{{\mathcal C_{\mathcal L}}}

We now place ourselves in a more general context where kinds are either variables
or constants belonging to a total bounded lattice $(\mathcal L, \leq_{\mathcal L})$ ie.,
a lattice which admits a total order and upper and lower bounds ($l^\top$ and $l^\bot$).
We note lattice elements $l$ and $\glb_i l_i$ (resp. $\lub_i l_i$)
the greatest lower bound (resp. least upper bound) in $\mathcal L$.
%
Let $\CL$ the set of constraints in this lattice. We consider the
following base entailment rules in this system:
\begin{center}
  \begin{mathpar}
    \inferrule{l \leq_{\mathcal L} l'}{\entail{}{\Cleq{l}{l'}}}
    \and
    \inferrule{}{\entail{}{\Cleq{k}{l^\top}}}
    \and
    \inferrule{}{\entail{}{\Cleq{l^\bot}{k}}}
  \end{mathpar}
\end{center}

>>>>

\begin{figure*}[tp]
  \input{infer/lattice}
  \caption{Lattice inequalities -- $k \lk_\Lat k'$}
  \input{infer/entails}
  \caption{Base entailment rules -- $\entail{C}{D}$ }
  \label{rules:entail}
\end{figure*}

@@

\begin{figure}[tp]\centering
\begin{mathpar}
  % \Sv\cap\Sv'
  % &= \left\{ x \to l,l'
  %   \mid \Sone{x}{l}\in\Sv \text{ and } \Sone{x}{l'}\in\Sv' \right\} \\
  \infer
  { \forall x \in \Dom{\Sv_1}\cup\Dom{\Sv_2}.\quad
    \tsplit{C_x}{\Sv(x)}{\Sv_1(x)}{\Sv_2(x)}
  } 
  { \tsplit{\bigwedge C_x}{\Sv}{\Sv_1}{\Sv_2} }
  % &= \Sv\cap\Sv' \sqcup
  %   (\Sv\Sdel{x' \mid x'\in\Sv'}) \sqcup
  %   (\Sv'\Sdel{x \mid x\in\Sv})
  %   &\text{where $\sqcup$ is the disjoint union}\\
  \and
  \inferrule{}
  { \Cleq{\Sv}{k_0}
    = \bigwedge_{\Sone{x}{l_x}\in\Sv} \bigwedge_{k\in l_x} \Cleq{k}{k_0}
  }
\end{mathpar}
\caption{Operation on usage maps $\Sv$}
\label{op:usgmap}
\end{figure}

@@

We now place ourselves in a more general context where kinds are either variables
or constants belonging to a total bounded lattice $(\mathcal L, \lk_\Lat)$ ie.,
a lattice which admits a total order and upper and lower bounds ($l^\top$ and $l^\bot$).
We note lattice elements $l$ and $\glb_i l_i$ (resp. $\lub_i l_i$)
the greatest lower bound (resp. least upper bound) in $\mathcal L$.
%
Let $\CL$ the set of constraints in this lattice. We consider the
following base entailment rules in this system:
\begin{center}
  \begin{mathpar}
    \inferrule{l \lk_\Lat l'}{\entail{}{\Cleq{l}{l'}}}
    \and
    \inferrule{}{\entail{}{\Cleq{k}{l^\top}}}
    \and
    \inferrule{}{\entail{}{\Cleq{l^\bot}{k}}}
  \end{mathpar}
\end{center}
